---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(badger)
library(dplyr)
library(UIWrangleR)
library(rmarkdown)
library(kableExtra)
```

# UIWrangleR

<!-- badges: start -->
```{r, echo=FALSE, results='asis'}
cat(
  badge_cran_release("badger", "green"),
  badger::badge_license(color = "blue")
)
```

<!-- badges: end -->

The goal of UIWrangleR is to to facilitate while standardizing common functions and processes used by the University of Idaho Advancement Services Data Team.

## Installation

You can install the development version of UIWrangleR like so:

``` r
install.packages("devtools")
devtools::install_github("https://github.com/jwisaacson41/UIWrangleR")
```

## Functions

### `household_fix`

The `household_fix` function helps to fill in NA values with the values of another column. The most common instance is where married individuals will have a primary individual listed. Single individuals typically do not have a `household_primary` ID listed as shown below.

```{r}
starwars_donors[c(1:3, 90:93),] %>%
  kable() %>%
  kable_styling()
```

Using the function we can quickly reconcile the field to ensure all individuals have a value in the `Household_Primary` column.

```{r}
starwars_donors[c(1:3, 90:93),] %>%
  mutate(Household_Primary = household_fix(Household_Primary, Primary_ID)) %>%
  kable() %>%
  kable_styling()
```


## Data Sets

